Transfer learning for \'echelle spectroscopy with \texttt{blas\'e}

### 2022-06-22 paper/paper1/ms.tex
Add regularization matrh

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=0.45\textwidth]{figures/N_lines_vs_Teff_prom.png}
    \includegraphics[width=0.45\textwidth]{figures/line_density_demo.png}
    \caption{Scaling of prominence and density of spectral lines.  
    \emph{Left:} Number of lines versus effective temperature for PHOENIX models truncated to IGRINS (\textbf{blue, connected} points) and HPF (\emph{red, free-standing} points) bandwidths, for different prominence thresholds of $0.02$, $0.01$, and $0.005$.
    \textbf{Right:} Number of lines per 100 \AA\ wavelength bin for stellar (\emph{blue, upper envelope of steps}) and telluric (\emph{orange, lower envelope of steps}), illustrated for a $T_\mathrm{eff}=4700$~K, $\log{g}=4.5$ PHOENIX model and a $T=290 \mathrm{K}$, relative humidity of 40\% TelFit model.}
    \label{fig_Nlines_vs_teff}
\end{figure}

@@

Equation \ref{eqn_final_model} has up to $N_{\mathrm{lines}}\times3 \sim20,000$ tunabale parameters from the star, $N_{\mathrm{lines}}\times3 \sim15,000$ tunabale parameters from the Earth's atmosphere, plus $v\sin{i}$ and $RV$.  That adds up to 35,002 model parameters.  The resolving power may also be treated as tunable if it is not known or varies slightly with \emph{e.g.} seeing, slit-or-fiber illumination, or instrumental configuration.

@@

Even still, the regularization step is in some ways the most subjective, since the degree of regularization will control the degree of overfitting or underfitting. The most extreme regularization---the antithesis of the \emph{laissez-faire} scenario---would yield a model too rigid to respond to the data at all, yielding a model entirely unchanged from the cloned PHOENIX and \texttt{TelFit} models.  So regularization constitutes the only hyperparameters worthy of tuning in \texttt{blas\'e}.  The choice of how to set the regularization is problem-specific.  We default to the following choice. We fix all line parameters except for amplitude, which receives a regularization of 0.01, meaning that its amplitude should be within about 1\% of its cloned value.  The extrinsic $v\sin{i}$ and $RV$ have no regularization, but in practice, they need to be initialized close to their plausible values.

>>>>

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=0.45\textwidth]{figures/N_lines_vs_Teff_prom.png}
    \includegraphics[width=0.45\textwidth]{figures/N_lines_vs_Teff_prom.png}
    %\includegraphics[width=0.45\textwidth]{figures/line_density_demo.png}
    \caption{Scaling of prominence and density of spectral lines.
        \emph{Left:} Number of lines versus effective temperature for PHOENIX models truncated to IGRINS (\textbf{blue, connected} points) and HPF (\emph{red, free-standing} points) bandwidths, for different prominence thresholds of $0.02$, $0.01$, and $0.005$.
        \textbf{Right:} Number of lines per 100 \AA\ wavelength bin for stellar (\emph{blue, upper envelope of steps}) and telluric (\emph{orange, lower envelope of steps}), illustrated for a $T_\mathrm{eff}=4700$~K, $\log{g}=4.5$ PHOENIX model and a $T=290 \mathrm{K}$, relative humidity of 40\% TelFit model.}
    \label{fig_Nlines_vs_teff}
\end{figure}

@@

Equation \ref{eqn_final_model} has up to $N_{\mathrm{lines}}\times3 \sim20,000$ tunable parameters from the star, $N_{\mathrm{lines}}\times3 \sim15,000$ tunable parameters from the Earth's atmosphere, plus $v\sin{i}$ and $RV$.  That adds up to 35,002 model parameters.  The resolving power may also be treated as tunable if it is not known or varies slightly with \emph{e.g.} seeing, slit-or-fiber illumination, or instrumental configuration.

@@

Even still, the regularization step is in some ways the most subjective, since the degree of regularization will control the degree of overfitting or underfitting. The most extreme regularization---the antithesis of the \emph{laissez-faire} scenario---would yield a model too rigid to respond to the data at all, yielding a model entirely unchanged from the cloned PHOENIX and \texttt{TelFit} models.  So regularization constitutes the only hyperparameters worthy of tuning in \texttt{blas\'e}.  The choice of how to set the regularization is problem-specific.  We default to the following choice. We usually fix all line parameters except for amplitude, which receives a log-normal distribution:

\begin{eqnarray}
    \mathrm{regularization} \equiv \ln{\mathrm{prior}}  = \frac{1}{2} \sum_{j=1}^{N_\mathrm{lines}} \Big(\frac{\ln{a_j} - \ln{a^\prime_j }}{\Lambda}\Big)^2
\end{eqnarray}

where the prime notation demarcates the amplitudes obtained from cloning, or the ``initial amplitude''.  We assign $\Lambda_{\ln{a}}\sim5$.  This weak degree of regularization has the effect of permitting refinement of only the most conspicuous data-model mismatches; the weakest lines don't both to move from their initial state because doing so would penalize the regularization penalty without enough reduction of the overall loss.  The extrinsic $v\sin{i}$ and $RV$ have no regularization, but in practice, they need to be initialized close to their plausible values.
